---
title: "Evaluating bee habitat provisioning within agricultural landscapes"
author: "Morgan Mackert"
date: "December 9, 2016"
output: word_document
---

The overarching goal of my research is to determine what influence contour buffer and filter strips in agricultural fields have on the abundance and diversity of the native bee community in the surrounding area.

View the bee data.
```{r bees, echo = FALSE}
setwd("C:/Users/Morgan/Documents/ISU/Semester 3/R/mmackert/Data")
simplebees <- read.csv("bees/working/simplebees.csv", header =T)
summary(simplebees)
```

Plot the bee data to look for outliers.
```{r bee outliers, echo = FALSE}
setwd("C:/Users/Morgan/Documents/ISU/Semester 3/R/mmackert/Data")
simplebees <- read.csv("bees/working/simplebees.csv", header =T)
boxplot(simplebees$TotalBees ~ simplebees$Site, xlab = "Site", ylab = "Number of Individuals", main = "Number of Bee Specimens by Site")
```

View the plant data.
```{r plants, echo = FALSE}
setwd("C:/Users/Morgan/Documents/ISU/Semester 3/R/mmackert/Data")
simpleplants <- read.csv("plants/working/simpleplants.csv", header = T)
summary(simpleplants)
```

Plot the plant data to look for outliers.
```{r plant outliers, echo = FALSE}
setwd("C:/Users/Morgan/Documents/ISU/Semester 3/R/mmackert/Data")
simpleplants <- read.csv("plants/working/simpleplants.csv", header = T)
boxplot(simpleplants$TotalPlants ~ simpleplants$Site, xlab = "Site", ylab = "Number of Species", main = "Number of Plant Species by Site")
```

The best general linear model as of now is as follows. It includes Site as well as an interaction between Date and plant species richness.
```{r glm, eval = FALSE}
setwd("C:/Users/Morgan/Documents/ISU/Semester 3/R/mmackert/Data")
beesvsplantsbysitedate <- glm(formula = simplebees$TotalBees ~ simplebees$Date * simpleplants$TotalPlants + simplebees$Site, family = poisson)
summary(beesvsplantsbysitedate)
```
